Succinct Representations for Abstract Interpretation

### 2011-11-04 papers/PLDI2012/implicitization.tex
capitalize
rephrase 2.3

\newcommand{\MM}[1]{{\color{blue} TODO(MM): #1}}
\newcommand{\JH}[1]{{\color{teal} TODO(JH): #1}}
\newcommand{\DM}[1]{{\color{violet} TODO(DM): #1}}
%\newcommand{\MM}[1]{}
%\newcommand{\JH}[1]{}
%\newcommand{\DM}[1]{}

@@

\title{Succinct representations for abstract interpretation}
\subtitle{Combined analysis algorithms and experimental evaluation}

@@

Classical interval analysis on this program yields $\lstinline|x_old| \in [-100000,100000]$.
We have transformed the first program into the second, manually pruning out infeasible paths; yet in general the resulting program could be exponentially larger than the first (as in Fig.~\ref{fig:multigraph}), even though not all feasible paths are needed to compute the invariant.
Following recent suggestions \cite{Gawlitza_Monniaux_ESOP11,Monniaux_Gonnord_SAS11}, we avoid this space explosion by keeping the second program implicit while simulating its analysis. This means we work on an implicitly represented transition multigraph (Fig.~\ref{fig:multigraph}); its compact representation is given by the transition graph of the first program.

Contribution \ref{contr:disjunctive} (\S\ref{sec:disjunctive}) replaces the exponential expansion of disjunctive invariant generation from \citet{DBLP:conf/pldi/GulwaniZ10} by an implicit representation;
contribution \ref{contr:guided_multigraph} (\S\ref{sec:guided_multigraph}) recasts the ``guided analysis'' from \citet{DBLP:conf/sas/GopanR07} on an implicit representation of the paths in lieu of the individual transitions.

>>>>

%\newcommand{\MM}[1]{{\color{blue} TODO(MM): #1}}
%\newcommand{\JH}[1]{{\color{teal} TODO(JH): #1}}
%\newcommand{\DM}[1]{{\color{violet} TODO(DM): #1}}
\newcommand{\MM}[1]{}
\newcommand{\JH}[1]{}
\newcommand{\DM}[1]{}

@@

\title{Succinct Representations for Abstract Interpretation}
\subtitle{Combined analysis algorithms and experimental evaluation}

@@

Classical interval analysis on this program yields $\lstinline|x_old| \in [-100000,100000]$.
We have transformed the first program into the second, manually pruning out infeasible paths; yet in general the resulting program could be exponentially larger than the first (as in Fig.~\ref{fig:multigraph}), even though not all feasible paths are needed to compute the invariant.

Following recent suggestions \cite{Gawlitza_Monniaux_ESOP11,Monniaux_Gonnord_SAS11}, we avoid this space explosion by keeping the second program implicit while simulating its analysis. This means we work on an implicitly represented transition multigraph (Fig.~\ref{fig:multigraph}); it is succinctly representated by the transition graph of the first program.
Our first contribution (\S\ref{sec:guided_multigraph}) is to recast the ``guided analysis'' from \citet{DBLP:conf/sas/GopanR07} on such a succinct representation of the paths in lieu of the individual transitions.
A similar explosion occurs in disjunctive invariant generation, following \citet{DBLP:conf/pldi/GulwaniZ10}; our second contribution (\S\ref{sec:disjunctive}) applies our implicit representation to their method.
